Breast Cancer Diagnosis Classification Analysis

### 2022-12-09 powerpoint.rmd
updated_pp

@@

@@

![Best Model was Ridge Regression](area_mean.png){

@@

>>>>

## Diagnosis Distribution

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
# There are more benign tumors than malignant tumors
# histogram of diagnosis
edaData <- read_csv("breast_cancer_diagnostic_data.csv")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(edaData) +
  geom_bar(aes(x = diagnosis), fill = "#c82798") +
  labs(x = "Diagnosis", y = "Count", title = "Count of Diagnosis") +
  theme(axis.text = element_text(size = 20), axis.title = element_text(size = 30), plot.title = element_text(size = 30))
```

@@

# Support Vector Machines

@@

![Best Model was Ridge Regression](area_mean.png)

@@

- More data points (more observations)
- More features (more variables)
- More proccessing power
